\documentclass{thesis/resources/ituthesis}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{svg}
\usepackage{calc}
\usepackage{fancyvrb}
\usepackage{multirow}
\usepackage{lscape}
\usepackage{longtable}
\usepackage{hyperref}

\settitle{Testing Faster in\\ Continuous Integration Pipelines. \\An Industrial Case Study}
\setauthor{Diego Joshua Martínez Pineda}
\setsupervisor{Mahsa Varshosaz}
\setdate{May 2022}

\begin{document}

\frontmatter

\thetitlepage
\newpage
\chapter{\texttt{SYN/ACK}$^1$}
\footnotetext[1]{A TCP joke, because less people would get a UDP one.\footnotemark[2]}
\footnotetext[2]{Yes, that was another joke.}

\parbox{0.8\textwidth}{
Oh... so many things to acknowledge and be thankful about. It transcends words really.

Thanks to the kind people and great engineers at Microsoft, it is an honor to be able to learn
from all of you. Thanks to the team behind the ITU's HPC, always helpful and effective. 
And thanks to Mahsa, my supervisor, for her extensive proofreading, and guidance throughout 
the project, I truly appreciate it. 
}

\vspace{3.5cm}

\parbox{\textwidth}{
    \begin{flushright}
``Gracias" no son suficientes para las personas que me han ayudado de la manera 
m\'as profunda. Gracias a mis abuelos Abel y Ana Mar\'ia, por su amor y sabidur\'ia.
Gracias a Sof\'ia, Elisa, Miguel y Anabelle, la familia que me ha hecho quien soy y 
que me ha ense\~nado lo que significa dar desinteresadamente. 

Finalmente, gracias a la familia que me ha dado vital apoyo en esta etapa de mi vida. Gracias a 
mis primos Karla y Oskar, a mi t\'ia Patricia por toda su entrega, amor y paciencia. A mi t\'io, Anders S\o{}rensen, 
osito, que me ense\~n\'o tanto en tan poco tiempo. Continuo aprendiendo de ti, te admiro, extra\~no 
y llevo en mi coraz\'on por el resto de mi vida.  

M\'as alla de las palabras, los amo. Todos mis logros son en verdad suyos.
    \end{flushright}
}

\newpage
\thispagestyle{empty}
\begin{abstract}
In this project, we present the evaluation of test selection and prioritization techniques, with data 
collected from a Continuous Integration (CI) pipeline of the Microsoft \emph{Business Central} project.

Having an effective technique for test prioritization in a project is relevant in Continuous Integration
pipelines. Their execution can be time-consuming and energy inefficient. Furthermore, these are typically executed
multiple times per day in a large team. Speed and efficiency not only benefit the development cycles but overall development
costs and energy impact.

We reduce the test prioritization problem to a ranking problem. This is done by extracting 
numeric representations of the changes in a codebase, and using them as input vectors to 
different ranking algorithms. In contrast to existing research, we use different representations;
most notably, the usage of test coverage information. 

Our results show that for the datasets created, using coverage information for assigning priorities 
increases the effectiveness of the prioritization used. However, using coverage information for representing 
changes reduced its effectiveness. 

Based on our results, we argue that with this approach to prioritization we would be able to reduce 
the number of tests that were run by 60\% using a conservative estimate of the best performing algorithm,
which corresponds to an execution time improvement of 90\% in average. This suggests that these approaches
are well suited for the pipeline under study.

Furthermore, we also give an outline of how this prioritization could be used in different stages 
of the existing pipeline.
\end{abstract}

\newpage
\tableofcontents

\mainmatter

\input{thesis/01-Introduction/chapter}%
\input{thesis/02-Background/chapter}%
\input{thesis/03-Method/chapter}%
\input{thesis/04-Results/chapter}%
\input{thesis/05-Conclusion/chapter}%
\input{thesis/06-FutureWork/chapter}%
\bibliographystyle{plain}
\bibliography{thesis/references}
\input{thesis/0A-appendix/appendix}%

\end{document}